Simple and robust inference of connectomes using partial correlation coefficients

### 2014-06-10 article.tex
smaller abstract (remove \)

\begin{abstract} Understanding how the brain works is a key to understand and
to treat brain pathologies and disorders such as Parkinson's disease,
epilepsy. Retrieving the connectomes, neurons connectivity map, will shed new
lights on the anatomical and functional connectivity of the brain.\\ In the
context of the Connectomics challenge, we propose a simple  algorithm made of
four stages, using preprocessing and partial correlation to achieve a network
inference of high quality.\\ We put in perspective our method by comparing
with other inference method such as GTE \cite{stetter2012model}, another
method proposed to infer a neural network from calcium fluorescent imaging,
and Genie3 [], a tree-based approach very competitive in several gene
inference challenge (i.e. DREAM4 and DREAM5).\\

>>>>

\begin{abstract} Understanding how the brain works is a key to understand and
to treat brain pathologies and disorders such as Parkinson's disease,
epilepsy. Retrieving the connectomes, neurons connectivity map, will shed new
lights on the anatomical and functional connectivity of the brain. In the
context of the Connectomics challenge, we propose a simple  algorithm made of
four stages, using preprocessing and partial correlation to achieve a network
inference of high quality. We put in perspective our method by comparing
with other inference method such as GTE \cite{stetter2012model}, another
method proposed to infer a neural network from calcium fluorescent imaging,
and Genie3 [], a tree-based approach very competitive in several gene
inference challenge (i.e. DREAM4 and DREAM5).
